---
title: "HW4"
author: "iganelin"
date: "October 4, 2017"
output: html_document
  github_document: default
---
# Homework 4

### Loading libraries
```{r}
library(gapminder)
library(tidyverse)
library(knitr)
library(dplyr)
```

## Activity #1:  Minimal guide to tidyr

This is a minimal guide, mostly for myself, to remind me of the most import tidyr functions **gather** and **spread** functions that I'm familiar with. Also checkout [A tidyr Tutorial](http://data.library.virginia.edu/a-tidyr-tutorial/)

Start with installing the package:
```{r}
install.packages("tidyverse")
install.packages("tidyr")
library(tidyr)
library(gapminder)
```
We will be using the **gapminder** data as our input.
- Firstly, let's create a data frame to manipulate with:
```{r}
dp <- gapminder %>%
  group_by(continent) %>% 
  summarize(mean_gdpPercap = mean(gdpPercap),
              n_countries    = length(gdpPercap))

continents <- data.frame(
   continent = dp$continent,
   meanGdp   = dp$mean_gdpPercap,
   n_countries = dp$n_countries)
continents 
```
- The help page for gather says that it “takes multiple columns and collapses into key-value pairs, duplicating all other columns as needed.”
```{r}
continentsG <- gather(data = continents, key = continent, value = meanGdp)
continentsG
```

