---
title: "Class 10"
author: "Rainer"
date: "10/5/2017"
output: html_document
---
Getting my dev tools on
```{r}
install.packages("devtools")
library(devtools)
library(tidyverse)
install_github("JoeyBernhardt/singer")
```

Now we have the singer dataframes! Huzzah

```{r}
library(singer)
# Load songs into the environment
data("locations")
data("songs")
```

and we can give a look at them!!

```{r}
glimpse(songs)
glimpse(locations)
```

```{r}
View(songs)
View(locations)
```




### Release and Year

Produce a dataframe with all the albums, the artists and the year in which the album was published

```{r}
release_year <- inner_join(locations,songs,by=c("title","artist_name"))%>% 
  select(release, artist_name,year)

View(release_year)
View(inner_join(locations,songs,by="title"))
```

### Challenge 1

Get the number of releases per year

```{r}
inner_join(songs,locations,by="title") %>% 
  count(year)
```


## Reshaping
```{r}
data("singer_locations")
glimpse(singer_locations)

View(singer_locations)

```

year, artist_hotttnesss, artist_familiarity, duration

```{r}
hfd_y <- singer_locations %>% 
  select(year, artist_hotttnesss, artist_familiarity,duration)

hfd_y %>% 
  filter(artist_hotttnesss>0) %>% 
  ggplot(aes(x=artist_hotttnesss,y=artist_familiarity))+geom_point()
```

package 'tidyr', 'gather' - transforms data from a wide format into a long format. It stacks the values on top of each other

```{r}

hfd_y_long <- hfd_y %>% 
  gather(key="Measure", value="Units", artist_hotttnesss:duration)

# View(hfd_y)
# View(hfd_y_long)

hfd_y_long %>% 
  filter(year > 0) %>% 
  ggplot(aes(x=year,y=Units))+
  geom_point()+
  facet_wrap(~ Measure, scales="free")
```


we get the same year, the measure (name of the column) and its value





