---
title: "cm101-547"
author: "IG"
date: "October 24, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
my_string <- "Surroundded by quotes."
my_string
my_string2 <- 'Tis is anothes string'
my_string2
my_string3 <- " a slash \ "
my_string3
```

### HW
How do I "string"" a single slash?

```{r}
my_string4 <- `my_string`  # it is just a naming of an object
my_string5 <- 'my_string'  # this is the assignment of the string to the object
my_string4 == my_string5
my_string6 <- "my_string"
my_string5 == my_string6


```
```{r}
#devtools::install_github("joeybernhardt/singer")
library(singer)
places <- unique(singer_locations$city)

str(places)
nchar(c("City", "double", "a very long string")) #counts the length of the strings
nchar(c("", NA, " ", "   "))

```

## The tools of the trade
```{r}
devtools::install_github("tidyverse/stringr")
devtools::install_github("tidyverse/glue")
library(tidyverse)
library(stringr)
library(glue)
```

glueing `glue()`

```{r}
My_name <- "Giulio"
My_age <- 109
My_color <-"blue"

glue("Myname is {My_name}", "My age two years ago was {My_age - 2},")
```
```{r}
paste("My name is ", My_name,", My age was ", My_age - 2)
```
Writes on different lines
```{r}
glue("
     Myname is 
{My_name} ", 
" My age two years ago was 
{My_age - 2}",
My_name = "Another Name",
My_age = 10
     )

```
## Challenge

Phrase : Today is Wednesday, October 29, 1986 and the sun shines
```{r}
today <- Sys.Date()
today_frmt <- format(today, format="%A, %B %d, %Y")
phrase <- "Today is {today_frmt} and the sun shines"

glue(phrase)
```
```{r}
singer_locations %>% 
  glue_data("{artist_name} is from {city}.") %>% 
  head()
```

### Stringr

```{r}
library(stringr)
getNamespaceExports("stringr") #spits al teh functions in the package
```

```{r}
getNamespaceExports("stringr") %>%
  str_subset("str_")

getNamespaceExports("stringr") %>%
  str_view("str_")
```
### Challenge
Used to clean data frame
```{r}
places <- unique(singer_locations$city)

```
And let's get all the placeds containing the string "york".
```{r}
places %>% 
  str_to_lower() %>% 
  str_subset("york")
```
### Regular Expressions
```{r}
places %>% 
  str_subset("[Yyb]ork")
```

coll options with ignore_case == TRUE
```{r}
places %>% 
  str_subset(coll("york", ignore_case = TRUE))
```
At the END of the string
```{r}
places %>% 
  str_subset("York$")
```
At the START of the string
```{r}
places %>% 
  str_subset("^York")
```
### Challenge

Places that contain a digit in their names
```{r}
places %>% 
  str_subset("[:digit:]")

```
DOT replaces any character
?one or zero
+ at least one
{2} two appearances
* zero one or more

```{r}
places %>% 
  str_subset("B.a?")
places %>% 
  str_subset("B.a_+")
```

