---
title: "hw2"
author: "iganelin"
date: "September 20, 2017"
output: github_document
---
# Homework 2
```{r}
library(gapminder)
library(tidyverse)
```

## Smell test the data
- Is it a data.frame, a matrix, a vector, a list?
```{r}
typeof(gapminder) #list
head(gapminder) 
```
- How many variables/columns?
- How many rows/observations?
- Can you get these facts about “extent” or “size” in more than one way? 
```{r}
dim(gapminder)  # rows x cols: 1704x6
ncol(gapminder) # 6
nrow(gapminder) # 1704
```
- What data type is each variable?
```{r}
typeof(gapminder$country)   # integer
typeof(gapminder$continent) # integer
typeof(gapminder$year)      # integer
typeof(gapminder$lifeExp)   # double
typeof(gapminder$pop)       # integer
typeof(gapminder$gdpPercap) # double
```

# Explore individual variables
- What are possible values (or range, whichever is appropriate) of each variable?
```{r}
summary(gapminder$year)
```
- What values are typical? What’s the spread? What’s the distribution? Etc., tailored to the variable at hand.

*Mean: 1980, spread: from 1952 till 2007*
- Distribution:
```{r}
hist(gapminder$year)
```

# Explore various plot types
- A scatterplot of two quantitative variables.
```{r}
ggplot(gapminder, aes(x = year, y = lifeExp)) + geom_point()
ggplot(gapminder, aes(x = year, y = gdpPercap)) + geom_point()
```

- A plot of one quantitative variable. Maybe a histogram or densityplot or frequency polygon.
```{r}
hist(gapminder$lifeExp)
```


- A plot of one quantitative variable and one categorical. Maybe boxplots for several continents or countries.
```{r}
ggplot(gapminder, aes(x = continent, y = lifeExp)) + geom_boxplot()
```

# Use filter(), select() and %>%

- Use filter() to create data subsets that you want to plot.
```{r}
filter(gapminder, continent=="Asia" & pop>=2.960e+07)
filter(gapminder, continent=="Asia")
```

- Practice piping together filter() and select(). Possibly even piping into ggplot().
```{r}
gapminder %>% 
  filter(continent=="Asia" & pop>=2.960e+07) %>% 
  select(-gdpPercap)
```

# But I want to do more!



