---
title: "hw2"
author: "iganelin"
date: "September 20, 2017"
output: md_document
---
# Homework 2

Loading libraries
```{r}
library(gapminder)
library(tidyverse)
library(knitr)
library(dplyr)
```

## Smell test the data
- Is it a data.frame, a matrix, a vector, a list?
```{r}
typeof(gapminder) #list
head(gapminder) 
```
- How many variables/columns?
- How many rows/observations?
- Can you get these facts about “extent” or “size” in more than one way? 
```{r}
dim(gapminder)  # rows x cols: 1704x6
ncol(gapminder) # 6
nrow(gapminder) # 1704
```
- What data type is each variable?
```{r}
typeof(gapminder$country)   # integer
typeof(gapminder$continent) # integer
typeof(gapminder$year)      # integer
typeof(gapminder$lifeExp)   # double
typeof(gapminder$pop)       # integer
typeof(gapminder$gdpPercap) # double
```

# Explore individual variables
- What are possible values (or range, whichever is appropriate) of each variable?
```{r}
summary(gapminder$year)
```
- What values are typical? What’s the spread? What’s the distribution? Etc., tailored to the variable at hand.

*Mean: 1980, spread: from 1952 till 2007*
- Distribution:
```{r}
hist(gapminder$year)
```

# Explore various plot types
- A scatterplot of two quantitative variables.
```{r}
ggplot(gapminder, aes(x = year, y = lifeExp)) + geom_point()
ggplot(gapminder, aes(x = year, y = gdpPercap)) + geom_point()
```

- A plot of one quantitative variable. Maybe a histogram or densityplot or frequency polygon.
```{r}
hist(gapminder$lifeExp)
```


- A plot of one quantitative variable and one categorical. Maybe boxplots for several continents or countries.
```{r}
ggplot(gapminder, aes(x = continent, y = lifeExp)) + geom_boxplot()
```

# Use filter(), select() and %>%

- Use filter() to create data subsets that you want to plot.
```{r}
filter(gapminder, continent=="Asia" & pop>=2.960e+07)
filter(gapminder, continent=="Asia")
```

- Practice piping together filter() and select(). Possibly even piping into ggplot().
```{r}
gapminder %>% 
  filter(continent=="Asia" & pop>=2.960e+07) %>% 
  select(-gdpPercap)
```

# But I want to do more!

Evaluate this code and describe the result. Presumably the analyst’s intent was to get the data for Rwanda and Afghanistan. Did they succeed? Why or why not? If not, what is the correct way to do this?
```{r}
filter(gapminder, country == c("Rwanda", "Afghanistan"))
```
Answer: No.

The right way would be:
```{r}
filter(gapminder, country %in% c("Rwanda", "Afghanistan"))
```

- Present numerical tables in a more attractive form, such as using knitr::kable().
```{r}
gapminder %>% 
  filter(country %in% c("Rwanda", "Afghanistan")) %>% 
  kable(., format = "markdown", caption = "Kable Rmd Good Looking Table")
```

- Use more of the dplyr functions for operating on a single table.
```{r}
gapminder %>% 
  filter(continent=="Asia" & pop>=2.960e+07) %>% 
  select(-pop) %>% 
  mutate(developpedCountries = gdpPercap>20000) %>% 
  kable(., format = "markdown", caption = "Kable Rmd Good Looking Table")
```

# Report your process
The instructions were easy to follow and with help of the search engine, all the right answers were easily found.

The helpful tutorials: 

- [r-bloggers.com](https://www.r-bloggers.com/data-manipulation-with-dplyr/)

- [http://t-redactyl.io](http://t-redactyl.io/blog/2016/04/creating-plots-in-r-using-ggplot2-part-10-boxplots.html)
