---
title: "hw03_dplyr-and-more-ggplot2s"
date: "September 26, 2017"
output: 
  github_document: default
  html_document:
  toc: true
---
  
```{r}
library(tidyverse)
library(gapminder)
library(dplyr)
library(ggplot2)
library(knitr)
library(dplyr)
```


# Tasks

### Get the maximum and minimum of GDP per capita for all continents.
```{r}
gapminder %>% 
  group_by(continent) %>% 
  mutate(gdpMin = min(gdpPercap), gdpMax = max(gdpPercap)) %>% 
  head() %>% 
  kable(., format = "markdown", caption = "Maximum and minimum of GDP per capita for all continents")

```

- First Table: I created additional columns named gdpMax and gdpMin on the original data frame grouped by continent.

```{r}
gapminder %>%
    group_by(continent) %>% 
    summarize(gdpMinK = min(gdpPercap),
              gdpMaxK = max(gdpPercap))
```

- Second Table: The table with the summary by continent.

```{r}
mn <- gapminder %>% 
  group_by(continent) %>% 
  mutate( gdpMin = min(gdpPercap), gdpMax = max(gdpPercap))

  ggplot(mn, aes(continent,gdpMax), colour=country) +
  geom_point() +
  theme_bw() +
  ggtitle("Maximum GDP")

  ggplot(mn, aes(continent,gdpMin), colour=country) +
  geom_point() +
  theme_bw() +
  ggtitle("Minimum GDP")
  
  ggplot(mn) +
  geom_crossbar(aes(ymin = gdpMin, ymax = gdpMax, x = continent, y = gdpPercap), fill = "blue",   fatten = 0) +
  theme_bw() +
  ggtitle("Crossbar")
```

- Two graphs displaying minimum and maximum values. Did some research on how to add the title to the graph.
- Crossbar graph showing min and Max. Played a bit with the fatten values and the colors.

### Look at the spread of GDP per capita within the continents.
```{r}
gapminder %>% 
  group_by(continent) %>% 
  mutate(gdpVar = var(gdpPercap), gdpMean = mean(gdpPercap)) %>% 
  head() %>% 
  kable(., format = "markdown", caption = "Spread of GDP per capita within the continents")
```

- First Table: I created additional columns named gdpMean and gdpVar on the original data frame grouped by continent. Print its head as kable just to see if it looks fine.

```{r}
gapminder %>%
    group_by(continent) %>% 
    summarize(gdpVarK = var(gdpPercap),
              gdpMeanK = mean(gdpPercap))

```

- Second Table: The table with the summary by continent. Very nice summary tibble, will definnitely integrate it into teh future workflow.

```{r}
mn <- gapminder %>% 
  mutate(gdpVar = var(gdpPercap), gdpMean = mean(gdpPercap))  %>% 
  ggplot(aes(continent,gdpPercap)) + 
  geom_boxplot()
mn + geom_point() +
  ggtitle("Mean and Variance GDP by Continent")

```
 
- Nice box plot, but I am not sure if the variance is displayed correctly. I played with the parameters, but will have to research it a bit more in the future. 
 
### How is life expectancy changing over time on different continents?
```{r}
gapminder %>% 
  arrange(continent) %>% 
  head() %>% 
  kable(., format = "markdown", caption = "Life expectancy by Continents")

gapminder %>% 
    ggplot(aes(year,lifeExp)) +
  facet_wrap(~ continent) +
  geom_point() +
  geom_smooth(method="lm", se=FALSE) +
  ggtitle("Life expectancy by Continents")

```

- From the graph we can see that the life expectancy grows on all the continents, but with different rate.


### Remaining Questions

- Compute a trimmed mean of life expectancy for different years. Or a weighted mean, weighting by population. Just try something other than the plain vanilla mean.
```{r}

```

- Report the absolute and/or relative abundance of countries with low life expectancy over time by continent: Compute some measure of worldwide life expectancy – you decide – a mean or median or some other quantile or perhaps your current age. Then determine how many countries on each continent have a life expectancy less than this benchmark, for each year.
```{r}

```
- Find countries with interesting stories. Open-ended and, therefore, hard. Promising but unsuccessful attempts are encouraged. This will generate interesting questions to follow up on in class.
```{r}

```
- Make up your own! Between the dplyr coverage in class and the list above, I think you get the idea.
```{r}

```

### Report your process
- A few web searches were required in order to find appropriate functionality for ggplot. I used the RStudio forums and stackoverflow.
- Three tables + three graphs are ready. Will add more if time permits.

*Thank you :)*