---
title: "STAT_547_HW10"
author: "iganelin"
date: "`r format(Sys.Date())`"
output: github_document
always_allow_html: yes
---
## HW10


#### We start with loading all the necessary general purpose libraries

```{r message=FALSE}
library(tidyverse)
library(magrittr)
library(purrr)
library(glue)
library(stringr)
library(purrr)
library(ggmap)
library(knitr)
```

#### Libraries for web scraping

```{r message=FALSE}
library(rvest)
library(xml2)
library(httr)
library(leaflet)
```
#### Working with the [OMDB API](https://www.omdbapi.com)

```{r message=FALSE}
get_movie <- function(title, year, key){
	query_string <- glue("http://www.omdbapi.com/?t={title}&y={year}&apikey={key}")
	movie_result <- httr::GET(query_string)
	movie_content <- as.data.frame(content(movie_result))
	return(movie_content)
}
```

#### Start with requesting the information of one of the movies you would like to see. For testing purposes only use your key. you can request it [here](https://www.omdbapi.com/apikey.aspx).

```{r message=FALSE}
movie_info <- get_movie("babe", "1995","33ffee5e")
typeof(movie_info)
knitr::kable(movie_info)
#View(movie_info)
```
#### Plot the Movies locatoin using simple ggmap.

```{r}
ggmap_movie_location <- function(movie_info){
	countries <- str_split(movie_info$Country, ",")
	loc <- geocode(as.character(countries))
	map_in <- get_map(location = c(lon = loc$lon, lat = loc$lat), zoom = 18, scale = "auto", maptype = "satellite")
	map_out <- ggmap(map_in)+geom_point(aes_string(x=loc$lat, y=loc$lon), colour = "red")
}
map <- ggmap_movie_location(movie_info)
map
```

#### Plot the Movie's of interest Location using ggmap and leaflet. Leaflet is better for html or shiny apps display of the data.

```{r}
get_movie_location <- function(movie_info){
	countries <- str_split(movie_info$Country, ",")
	loc <- geocode(as.character(countries))
	m <- leaflet() %>%
  		addTiles() %>%  # Add default OpenStreetMap map tiles
  		addMarkers(lng=loc$lon, lat=loc$lat, popup="Movie Location")
	return(m)
}

map <- get_movie_location(movie_info)
map
```

#### Expand our function to output multiple

```{r message=FALSE}
get_movies <- function(title, key){
	for (i in 1:length(movies_list)){
		if (i == 1){
			query_string <- glue("http://www.omdbapi.com/?t={movies_list[i]}&apikey={key}")
			movie_result <- httr::GET(query_string)
			movie_content <- as.data.frame(content(movie_result))
		}
		else{
			query_string <- glue("http://www.omdbapi.com/?t={movies_list[i]}&apikey={key}")
			movie_result <- httr::GET(query_string)
			movie_content <- full_join(movie_content, as.data.frame(content(movie_result)), by = colnames(as.data.frame(content(movie_result))))
		}
	}
	return(movie_content)
}
```

#### Let's see the result.
We start with creating a list of the movies we would like to download info for.


```{r message=FALSE, include=FALSE}
movies_list <- c("babe", "thor", "spiderman")
movies <- get_movies(movies_list, "33ffee5e")
#View(movies)
knitr::kable(movies)
```
So now we can download the movie info and save it into the dataframe that we can use later in the project.

#### We can plot the rating of the movies that we extracted.

```{r}
plot_rating <- function(movies){
	r1 <- str_split(movies$Ratings.Value.1, " ")
	r2 <- str_replace(r1, "%", "")
	Rating <- as.integer(r2)
	Rating[is.na(Rating)] <- 0
	
	movies %>%
		mutate(rating = Rating) %>% 
		ggplot(aes(x = Title, y = Rating), colour=Title) +
		ggtitle("Movies Rating") +
		theme_classic() +
		geom_point()
}

plot_rating(movies)
```



#### This is a current weather request at the location of the movie. Use your key from [here](https://openweathermap.org/api).
The functions reads the data frame that we aquired earlier from the movie data set, then it calls the weather API and gets the current weather report for that location.
Easy, but powerful!

```{r message=FALSE}
current_weather <- function(movie_info, key){
	countries <- str_split(movie_info$Country, ",")
	loc <- geocode(as.character(countries))
	lat <- loc$lat
	lon <- loc$lon
	query_string <- glue("api.openweathermap.org/data/2.5/weather?lat={lat}&lon={lon}&appid={key}")
	weather_result <- httr::GET(query_string)
	weather_content <- content(weather_result)
	movie_content <- as.data.frame(weather_content$weather)
	return(movie_content)
}
weather_api_key <- "0e9fe1be47a184a37d666778718248b1"
weather <- current_weather(movie_info, weather_api_key)
#View(weather)
knitr::kable(weather)
```

##### Start with requesting the information of one of the movies you would like to see from [here](https://www.theimdbapi.org/).

```{r message=FALSE}

```


### Following functions currently do not work, as I am waiting for the API key approval:

#### Download the movie information from another [source](https://www.theimdbapi.org/) 
```{r message=FALSE}
get_movie2 <- function(title, year){
	query_string <- glue("http://www.theimdbapi.org/api/find/movie?title={title}&year={year}")
	movie_result <- httr::GET(query_string)
	movie_content <- as.data.frame(content(movie_result)[[1]])
	return(movie_content)
}
```

#### Download the movie information from yet another [source](https://www.themoviedb.org) 
```{r}
get_movie3 <- function(title, year, key){
	query_string <- glue("https://api.themoviedb.org/3/movie/550?api_key={key}")
	movie_result <- httr::GET(query_string)
	movie_content <- as.data.frame(content(movie_result))
	return(movie_content)
}
```