---
title: "HW7"
author: "iganelin"
date: "`r format(Sys.Date())`"
output:
  github_document: default
---

#Homework 07: Data wrangling wrap up (Due date 10/11/17)

### Loading libraries
```{r message=FALSE}
library(gapminder)
library(singer)
library(tidyverse)
library(knitr)
library(forcats)
library(magrittr)
library(dplyr)
library(meme)
library(readr)
library(tidyr)
library(stringr)
library(ggplot2)
```

```{r message=FALSE, warning=FALSE, error=FALSE }
u <- "http://i0.kym-cdn.com/entries/icons/mobile/000/000/745/success.jpg"
#meme(u, "Homework 6", "Yes! Give me more!")
mmplot(u) + mm_caption("Homework 7", "Yes! Give me more!", color="purple")
```

## Big picture

- Write (or extract from a previous analysis) three or more R scripts to carry out a small data analysis.
- The output of the first script must be the input of the second, and so on.
- Something like this:
        First script: download some data.
        Second script: read the data, perform some analysis and write numerical data to file in CSV or TSV format.
        Third script: read the output of the second script, generate some figures and save them to files.
        Fourth script: an Rmd, actually, that presents original data, the statistical summaries, and/or the figures in a little report.
        A fifth script to rule them all, i.e. to run the others in sequence.

