---
title: "HW7"
author: "iganelin"
date: "`r format(Sys.Date())`"
output:
  github_document: default
---

#Homework 07: Data wrangling wrap up (Due date 10/11/17)

### Loading libraries
```{r message=FALSE}
library(gapminder)
library(singer)
library(tidyverse)
library(knitr)
library(forcats)
library(magrittr)
library(dplyr)
library(meme)
library(readr)
library(tidyr)
library(stringr)
library(ggplot2)
```

```{r message=FALSE, warning=FALSE, error=FALSE }
u <- "http://i0.kym-cdn.com/entries/icons/mobile/000/000/745/success.jpg"
#meme(u, "Homework 6", "Yes! Give me more!")
mmplot(u) + mm_caption("Homework 7", "Yes! Give me more!", color="purple")
```

## Big picture

##### Write (or extract from a previous analysis) three or more R scripts to carry out a small data analysis.
##### The output of the first script must be the input of the second, and so on.
##### Something like this:

- First script: download some data: [1_download_wind_data.r](https://github.com/ilgan/STAT545-hw-ganelin-ilya/blob/master/HW7/1_download_wind_data.r)
- Second script: read the data, perform some analysis and write numerical data to file in CSV or TSV forma: [2_clean_wind_data.r](https://github.com/ilgan/STAT545-hw-ganelin-ilya/blob/master/HW7/2_clean_wind_data.r)
- Third script: read the output of the second script, generate some figures and save them to files: [3_plot_wind_data.rmd](https://github.com/ilgan/STAT545-hw-ganelin-ilya/blob/master/HW7/3_plot_wind_data.rmd)
- Fourth script: an Rmd, actually, that presents original data, the statistical summaries, and/or the figures in a little report: [4_wind_data.rmd](https://github.com/ilgan/STAT545-hw-ganelin-ilya/blob/master/HW7/4_wind_data.rmd)
- A fifth script to rule them all, i.e. to run the others in sequence: [Makefile](https://github.com/ilgan/STAT545-hw-ganelin-ilya/blob/master/HW7/Makefile)

#### Output Files from the pipeline

- Media files are [here](https://github.com/ilgan/STAT545-hw-ganelin-ilya/tree/master/HW7/media)
        

